Evaluating the Capabilities of Lattice Boltzmann Method for non-Newtonian and Free-surface Flows towards Applications in Wellbore Cementing

### 2016-07-27 src/algorithm/streaming.tex
wrote some basic algorithms

\begin{algorithm}
\caption{Streaming} \label{algo:streaming}
\begin{algorithmic}[1]
\Procedure{streaming}{$f$}
Initialize temporary 3D array the size of lattice, $f_temp$
\EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
\caption{Streaming} \label{algo:streaming}
\begin{algorithmic}[1]
\Procedure{streaming}{$f$} \Comment{$f$ is a 3D Array of particle distributions}
\Statex \Comment{$f[k, i, j] \equiv f_k(\pos_{ij}, t)$}
\State Initialize temporary 3D array the size of lattice, $f_{temp}$
\Statex
\For{each node $(i, j)$}
  \For{each discrete velocity vector, $\pvel_k$}
    \If {$(i + \pvel_{k1} \Delta t, j + \pvel_{k2} \Delta t)$ is in bounds and is not a solid wall}
      \State $f_{temp}[k, i + \pvel_{k1} \Delta t, j + \pvel_{k2} \Delta t] = f[k, i, j]$
    \EndIf
  \EndFor
\EndFor
\Statex
\State \textbf{copy} $f_{temp}$ to $f$
\Statex
\EndProcedure
\end{algorithmic}
\end{algorithm}
